The \dealii Library, Version 9.4

### 2022-06-27 9.4/paper.tex
Add word

The new utility functions will be the building blocks for functions in 
the \texttt{NonMatching} namespace in future releases. While our current 
CutFEM implementation (see Section~\ref{sec:cut}) relies on a level set description of the domain to determine
the boundary and the quadrature rules, one could do that also based on non-matching overlapping
grids~\cite{massing2013efficient}, for which the newly introduced, CGAL-based Boolean operations and 
quadrature-generation functionality might be helpful.
The functionalities are applicable in a broad context of immersed problems, such as
for weakly imposing boundary conditions on the interface of an immersed boundary
using Nitsche's method and for coupling terms using Lagrange multipliers.

>>>>

The new utility functions will be the building blocks for functions in 
the \texttt{NonMatching} namespace in future releases. While our current 
CutFEM implementation (see Section~\ref{sec:cut}) relies on a level set description of the domain to determine
the boundary and the quadrature rules, one could do that also based on non-matching overlapping
grids~\cite{massing2013efficient}, for which the newly introduced, CGAL-based Boolean operations and 
quadrature-generation functionality might be helpful.
The functionalities are also applicable in a broad context of immersed problems, such as
for weakly imposing boundary conditions on the interface of an immersed boundary
using Nitsche's method and for coupling terms using Lagrange multipliers.
